\documentclass{resume}
\usepackage{xcolor}
\usepackage{enumitem}

\author{https://aravindvasu.dev}{Aravind Vasudevan}
\email{aravind\_vasudevan@outlook.com}
\phone{+14126087267}{(412) 608-7267}
\domain{https://aravindvasu.dev/about/}{https://aravindvasu.dev}
\github{https://github.com/AravindVasudev}{https://github.com/AravindVasudev}
\linkedin{https://www.linkedin.com/in/aravindvasudev/}{https://www.linkedin.com/in/aravindvasudev/}

\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Education}
\titlerule[0.2pt]
\noindent
\\
\textbf{Carnegie Mellon University -- School of Computer Science} \hfill \textit{Pittsburgh, PA} \\
{\small Master of Software Engineering -- Scalable Systems} \hfill \textit{\small December 2020}\\
\textit{\textbf{Coursework:} Distributed Systems, DevOps, Engineering Data Intensive Scalable Systems, Architecture for Software Systems, Introduction to Machine Learning, Analysis of Software Artifacts, Introduction to Computer Systems.}\\
%\textit{\textbf{Teaching Assistantship:} 17323/17623: Quality Assurance. October 2020 - December 2020.}\\
\\
\textbf{Anna University} \hfill \textit{Chennai, India} \\
{\small Bachelor of Engineering -- Computer Science \& Engineering} \hfill \textit{\small May 2018}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Experience}
\titlerule[0.2pt]
[margin=0.5in][margin=0.5in]
\\
\textbf{GoDaddy Inc.} \hfill \textit{Kirkland, WA (Remote)} \\
{\small Software Development Engineer II} \hfill \textit{\small March 2021 - Present}
\begin{itemize}
  \item Conceptualized a global control group feature which allows teams to access statistical impacts across a series of A/B tests.
  \item Integrated all our analytics services with monitoring tools to measure quality, availability, and performance of the product.
  \item Assembled a jenkins pipeline to test and auto-deploy projects using AWS CDK which is used by two new products.
\end{itemize}
\textbf{Carnegie Mellon University -- School of Computer Science} \hfill \textit{Pittsburgh, PA (Remote)} \\
{\small Teaching Assistant for 17323/17623: Quality Assurance} \hfill \textit{\small October 2020 - December 2020}
\begin{itemize}
  \item Conducted office hours to help students with their coursework/projects and evaluated the project submissions.
\end{itemize}
\textbf{GoDaddy Inc.} \hfill \textit{Kirkland, WA (Remote)} \\
{\small Intern --- Software Development Engineer} \hfill \textit{\small May 2020 - August 2020}
\begin{itemize}
  \item Reduced execution time of the analytics tool by two hours by redesigning it into multiple processes.
  \item Devised an AWS Batch based architecture to parallelize analysis in the analytics tool, which will further decrease runtime.
  \item Volunteered for the scrum master role to handle our project backlog on Jira, scrum meetings, and retrospective.
\end{itemize}
\textbf{Zoho Corporation} \hfill \textit{Chennai, India} \\
{\small Member Technical Staff} \hfill \textit{\small June 2018 - May 2019}
\begin{itemize}
  \item Simplified transaction handling by implementing an annotation-based framework using Aspect-Oriented Programming.
  \item Built an HTTP connection pool library that can share pools between modules separated across multiple codebases.
  \item Modularized i18n keysets by developing a library to load and validate keys across multiple repositories without collision.
  \item Distributed configuration across runtime-dependent repositories by building a tool to manage and validate conf files.
  \item Fixed distributed lock handling mechanism in Zoho CRM, which removed race-conditions between database operations.
\end{itemize}
\textbf{Zoho Corporation} \hfill \textit{Chennai, India} \\
{\small Project Trainee} \hfill \textit{\small December 2017 - March 2018}
\begin{itemize}
  \item Minimized dependency among teams by decoupling Zoho CRM into several compile-time independent components.
  \item Architected an observable-based inter-service communication framework that can resolve function calls at runtime.
\end{itemize}
\textbf{Tata Consultancy Services} \hfill \textit{Chennai, India} \\
{\small Project Intern} \hfill \textit{\small June 2017 - July 2017}
\begin{itemize}
  \item Prototyped a chatbot to simplify data lookup in Planatics, a financial data management tool, using RASA NLU and flask.
  \item Separated the chatbot service from the tool using microservice design-pattern and REST API for service interaction.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Academic Projects}
\titlerule[0.2pt]
\noindent
\\
\textbf{Distributed Bitcoin Miner} \hfill \textit{CMU Fall 2020}
\begin{itemize}
  \item Modeled an application layer protocol on top of UDP with resilience, liveness, and packet sequencing.
  \item Developed the protocol to be connection-oriented and support the client-server model natively.
  \item Implemented a distributed bitcoin miner system on top of this protocol with fault-tolerance.
  \item Designed the miner to be the client and the server to load-balance mining jobs using SRTF scheduling and chunking.
\end{itemize}
\textbf{Scalable Ecommerce Web Service} \hfill \textit{CMU Spring 2020}
\begin{itemize}
  \item Engineered a highly-scalable e-commerce app that can serve over a million requests/minute using EC2 and load balancer.
  \item Handled search functionality for around a million products using AWS RDS for storage and AWS ElastiCache for caching.
  \item Improved response time to under a second by devising a distributed in-memory caching framework.
  \item Synchronized the distributed cache using the check-on-use invalidation strategy and handled overflow using LRU eviction.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Skills}
\titlerule[0.2pt]
\noindent
\\
\textbf{Programming Languages:} Java, Python, Javascript, C, Bash, Go. \\
\textbf{Backend \& Database:} Node.js, Struts, Spring, Flask, MySQL, MongoDB, Redis, RabbitMQ. \\
\textbf{DevOps:} Docker, Jenkins, Vagrant, AWS stack, Ansible, Kubernetes. \\
\textbf{Frontend:} Angular, JQuery, SCSS, HTML, CSS.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}